\documentclass[review, 10pt]{elsarticle}
% \documentclass[preprint, 10pt]{elsarticle}

\usepackage{amsmath,amsthm,amsfonts,amssymb,mathtools}
\usepackage{graphicx} 
\usepackage[T1]{fontenc}
\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry} % Document margins
\usepackage{multicol} % Used for the two-column layout of the document
%%! Additional usepackage
\usepackage{physics}
\usepackage[hidelinks]{hyperref}
% \usepackage{hyperref} 
% \hypersetup{
	%     colorlinks=true,
	%     linkcolor=blue,
	%     filecolor=magenta,       
	%     urlcolor=cyan, 
	%     } 
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{float}
\usepackage[labelfont=bf]{caption} % Custom captions under/above floats in tables or figures

\usepackage{algorithm}% http://ctan.org/pkg/algorithms
\usepackage{algorithmicx} 
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

\usepackage{csquotes}
\usepackage{enumitem}
\usepackage{lineno}

\usepackage{xcolor}
\usepackage[draft]{changes}
\setauthormarkup{} % use empty author markup
\setdeletedmarkup{} % use empty deleted markup
\definecolor{harryModColor}{rgb}{0.8, 0, 0.3}
\definecolor{r1color}{rgb}{0.8, 0.1, 0.1}
\definecolor{r2color}{rgb}{0.1, 0.1, 0.8}
\definechangesauthor[name={Hanyu Zhou},color=harryModColor]{harry}
\definechangesauthor[name={Reviewer 1},color=r1color]{r1}
\definechangesauthor[name={Reviewer 2},color=r2color]{r2}
\definechangesauthor[name={Reviewer 1\&2},color=orange]{r12}
\usepackage{siunitx}

\journal{Journal of Computational Physics}

\begin{document}
	
\begin{frontmatter}
	
	%% Title, authors and addresses
	
	%% use the tnoteref command within \title for footnotes;
	%% use the tnotetext command for theassociated footnote;
	%% use the fnref command within \author or \address for footnotes;
	%% use the fntext command for theassociated footnote;
	%% use the corref command within \author for corresponding author footnotes;
	%% use the cortext command for theassociated footnote;
	%% use the ead command for the email address,
	%% and the form \ead[url] for the home page:
	%% \title{Title\tnoteref{label1}}
	%% \tnotetext[label1]{}
	%% \author{Name\corref{cor1}\fnref{label2}}
	%% \ead{email address}
	%% \ead[url]{home page}
	%% \fntext[label2]{}
	%% \cortext[cor1]{}
	%% \address{Address\fnref{label3}}
	%% \fntext[label3]{}

\title{Positivity-preserving implicit finite volume methods on unstructured grids for compressible flows}
% \title{Positivity-preserving algorithm for implicit finite volume methods simulating compressible flows}
% \title{Implicit positivity-preserving finite volume schemes on unstructured grids for compressible Euler and Navier-Stokes equations}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author[THU]{Hanyu Zhou}
\ead{zhy22@mails.tsinghua.edu.cn}
\author[CSRC]{Qian Wang\corref{cor1}}
\cortext[cor1]{Corresponding author.}
\ead{qian.wang@csrc.ac.cn}

\address[THU]{Department of Engineering Mechanics, Tsinghua University, Beijing 100084, China}
\address[CSRC]{Mechanics Division, Beijing Computational Science Research Center, Beijing 100193, China}
	
	
% \begin{abstract}
%     %% Text of abstract
%     \hspace{10pt}  
%     A frequently encountered issue in numerical simulations of complex compressible flows is the failure to preserve positivity of density or pressure, which leads to nonphysical solutions or numerical instabilities. It is a significant challenge to develop efficient and accurate positivity-preserving algorithms for numerical schemes with implicit time integration, where solutions are updated by solving nonlinear equations iteratively. To address this challenge, we propose a positivity-preserving algorithm for finite volume schemes with implicit time integration on unstructured grids. 
%     \replaced[id=r2]
%     {
%     In this algorithm, admissible cell averages are obtained by limiting time step sizes to control solution variations, 
%     while increment correction is introduced to directly enforce positivity 
%     during iteration.
%     }
%     {
%     In this algorithm, admissible cell averages are obtained by limiting time step sizes to control solution variations.
%     }
%     \replaced[id=r2]{
%     To overcome the difficulty of unknown solution changes in time step limiting, we employ a simple linear approximation to estimate the future state, based on the available residual of the semi-discrete finite volume scheme.}
%     {To overcome the difficulty of unknown solution changes in time step limiting, we employ explicit time discretization to efficiently estimate future states.} Allowable time step sizes are determined by constraining the relative solution changes to ensure the positivity of the updated solutions. Given positive cell averages, admissible reconstruction polynomials are obtained by using a scaling limiter. Importantly, the proposed positivity-preserving algorithm is also accuracy-preserving. This algorithm is applied to a high-order variational finite volume method with explicit first stage singly diagonally implicit Runge-Kutta (ESDIRK) time integration. Numerical results for a series of benchmark test cases demonstrate the high accuracy, high resolution,
%     \added[id=r2]{
%         high efficiency
%     }
%     and robustness of the positivity-preserving implicit high-order finite volume method. 
% \end{abstract}

\begin{abstract}
    %% Text of abstract
    \hspace{10pt}  
    A frequently encountered issue in numerical simulations of complex compressible flows is the failure to preserve positivity of density or pressure, which leads to nonphysical solutions or numerical instabilities. It is a significant challenge to develop efficient and accurate positivity-preserving algorithms for numerical schemes with implicit time integration, where solutions are updated by solving nonlinear equations iteratively. 
    \replaced[id=r2]
    {To address this challenge, we propose a positivity-preserving algorithm for finite volume schemes with implicit dual-time stepping on unstructured grids. 
    Given positive cell averages, admissible reconstruction polynomials can be obtained by using a scaling limiter. Therefore, the central objective of the algorithm is to preserve the positivity of cell averages throughout the implicit time integration, by enforcing admissibility of both the converged and all intermediate states during the iterative solution process.
    To achieve this, the physical time step is adaptively limited to guarantee the existence of an admissible solution at the next time level. To address the challenge posed by the unknown solution increment at the start of each time step, we employ a linear approximation based on the available residual of the semi-discrete finite volume scheme to estimate the future state. The allowable time step size is then determined by imposing a lower bound on this estimated state, with the lower bound chosen to exceed the estimation error, thereby ensuring the positivity of the future state. Additionally, time step limiting is applied in the pseudo-time direction, followed by an increment correction to maintain positivity of intermediate states during inner iterations. 
    }
    {To address this challenge, we propose a positivity-preserving algorithm for finite volume schemes with implicit time integration on unstructured grids. 
    In this algorithm, admissible cell averages are obtained by limiting time step sizes to control solution variations. To overcome the difficulty of unknown solution changes in time step limiting, we employ explicit time discretization to efficiently estimate future states.
   Allowable time step sizes are determined by constraining the relative solution changes to ensure the positivity of the updated solutions. Given positive cell averages, admissible reconstruction polynomials are obtained by using a scaling limiter.}
   Importantly, the proposed positivity-preserving algorithm is also accuracy-preserving. This algorithm is applied to a high-order variational finite volume method with explicit first stage singly diagonally implicit Runge-Kutta (ESDIRK) time integration. Numerical results for a series of benchmark test cases demonstrate the high accuracy, high resolution, \added[id=r2]{efficiency} and robustness of the positivity-preserving implicit high-order finite volume method. 
   \added[id=r2]{
    % The method exhibits high accuracy and resolution in positivity-preserving benchmark problems without sign of numerical failure.
    % In a real-life test problem with high-Reynolds hypersonic flow, the proposed implicit method, compared with an explicit method, is able to accelerate the computation by a factor of 140. 
    In a realistic high-Reynolds-number hypersonic flow test case, the positivity-preserving implicit finite volume method achieves a computational speedup of two orders of magnitude over its explicit counterpart.
   }
\end{abstract}

% The solution at next time level or next pseudo-time level, is unknown at the beginning of the time step or pseudo-time step, posing significant challenges for designing positivity-preserving algorithms. 
% To address this, we propose estimating the solution change over a time step using a simple linear approximation, where the estimated change is proportional to the time step size. The time step is then limited by imposing a lower bound on the estimated future state.
% If this lower bound exceeds the estimation error, the actual future state is guaranteed to remain positive.
	
\begin{keyword}
    %% keywords here, in the form: keyword \sep keyword
    Positivity-preserving algorithm \sep Finite volume method \sep Implicit time stepping \sep Accuracy-preserving property \sep Compressible flows
    %% PACS codes here, in the form: \PACS code \sep code
    
    %% MSC codes here, in the form: \MSC code \sep code
    %% or \MSC[2008] code \sep code (2000 is the default)
    
\end{keyword}
	
\end{frontmatter}

\linenumbers
\input{sections/introduction.tex}
\input{sections/implicitFV.tex}
\input{sections/ppAlgorithm.tex}
\input{sections/analysis.tex}
\input{sections/numResults.tex}
\input{sections/conclusions.tex}
\input{sections/acknowledgments.tex}
% \input{sections/appendix.tex}

%%%% BIBLIOGRAPHY
\bibliographystyle{elsarticle-num}
\bibliography{refs}

\end{document}
